---
title: "Four Cats Code"
author: "Erin Gillespie"
date: '2022-04-09'
output: pdf_document
---
Er
```{r}
#install.packages("tidyverse")
library(tidyverse)
#install.packages("zoo")
library(zoo)
gamer = read.csv("C:/Users/spgtff/Desktop/logs.csv")
gamerscore = gamer %>%
  filter(is.na(skill_level_priority) == FALSE)
SurveyResults = read.csv("C:/Users/spgtff/Desktop/S5_scores_cleaned.csv")
SurveyResults = SurveyResults %>%
  na.omit()
gamerinher = gamer %>%
  select(avatar_age, avatar_gender, avatar_id, avatar_name, player_id) %>%
  group_by(player_id) %>%
   mutate_all(funs(na.locf(., na.rm = FALSE)))
gamerinher = gamerinher %>% na.omit()%>%
distinct()
#write.csv(gamerscore, file = "Useful.csv")
prescolor = c("#8338ec")
```


```{r}
groupedgamers = gamerscore %>%
  group_by(player_id) 
gru1 = groupedgamers %>%
  filter(event_time_dbl == min(event_time_dbl)) %>%
  mutate(stend = "Begining")
gru2 = groupedgamers %>%
  filter(event_time_dbl == max(event_time_dbl))%>%
  mutate(stend = "Ending")
b4aft4 = left_join(gru1, gru2, by = "player_id")
rm(gru1)
rm(gru2)
rm(groupedgamers)
```

```{r}
#install.packages("viridis")
library(viridis)
idsss = as.data.frame(unique(gamer$player_id))
idsss = idsss %>%
  rename(player_id = `unique(gamer$player_id)`)
#unique(gamer$event_description)
eee = left_join(idsss, gamerinher, by= "player_id")
groupedgamers = left_join(gamerscore, eee, by = "player_id")
groupedgamers = groupedgamers %>% 
  filter(event_time_dbl < 50000)

ggplot(data = groupedgamers, mapping = aes(y = skill_level_people, x = event_time_dbl, col = skill_level_priority))+
  geom_jitter()+
   geom_smooth(method='lm') +
  labs(title = "Main skill growth over time", col = "Priority Skills")+
  xlab("Time Played")+
  ylab("People Skills")+ 
  scale_color_viridis_c(option = "plasma")
rm(groupedgamers)
rm(idsss)
rm(eee)
```

```{r}
SurveyResults = SurveyResults %>%
  group_by(player_id)
B6Aft6 = left_join(b4aft4, SurveyResults, by = "player_id")
doittho = lm(S5_mean ~ skill_level_know.y  + skill_level_me.y + skill_level_people.y + skill_level_priority.y + skill_level_refusal.y, data = B6Aft6)
summary(doittho)
rm(B6Aft6)
rm(b4aft4)
rm(doittho)
```


```{r}
namepie = as.data.frame(1:169)
namepie = namepie %>%
  mutate(Name = `1:169`) %>%
  mutate(Serious = ifelse(Name > 13, "Yes", "No"))
ggplot(data = namepie, mapping = aes(x = Serious))+
  geom_bar()
rm(namepie)
gamermaker = gamer %>%
  filter(event_description == "Player exits avatar creator")
gamermaker = left_join(gamermaker, gamerinher, by = "player_id")
ggplot(data = gamermaker, mapping = aes(x = event_time_dbl, fill = avatar_gender.y))+
  geom_histogram()+
  labs(title = "Time spent in avatar creation", fill = "Avatar Gender")  +
  xlab("Time in seconds") +
  ylab("Students")+
  scale_fill_viridis(option = "plasma", discrete = TRUE )
ggplot(data = gamermaker, mapping = aes(x = event_time_dbl, fill = avatar_id.y))+
  geom_histogram()+
  labs(title = "Time spent in avatar creation", fill = "Avatar race") +
  xlab("Time in seconds") +
  ylab("Students")+
  scale_fill_viridis(option = "plasma", discrete = TRUE )

rm(gamermaker)
```

Spen
```{r}
unique_survey_scores <- SurveyResults %>%
  distinct(player_id, .keep_all = TRUE)
```

```{r}
unique_survey_scores %>%
  ggplot(mapping = aes(x = S5_mean)) +
  geom_histogram() +
  xlab("Average Survey Response (1-4)") +
  ylab("Count") +
  theme_classic() +
  ggtitle("Average Response to Drug Use Resistance") +
  geom_vline(xintercept = mean(unique_survey_scores$S5_mean),
         	col = "blue",
         	lwd = 1) +
  annotate("text",
       	x = mean(unique_survey_scores$S5_mean) -.022,
       	y = mean(unique_survey_scores$S5_mean) * 10,
       	label = paste("Mean =", round(mean(unique_survey_scores$S5_mean), 3)),
       	col = "red",
       	size = 5)+
  scale_color_viridis(option = "plasma", discrete = TRUE )
```
```{r}
new_weeks <- SurveyResults %>%
  mutate(weeks = case_when(weeks == "0" ~ 'Zero',
                                   	weeks == "3" ~ 'Three',
                                   	weeks == "6" ~ 'Six',
                                   	weeks == "12" ~ 'Twelve',
                                   	weeks == "24" ~ 'Twenty Four'))
new_weeks %>%
  mutate(weeks = fct_relevel(weeks, "Zero", "Three", "Six", "Twelve", "Twenty Four")) %>%
  ggplot(mapping = aes(x = weeks, y = S5_mean, fill = weeks)) +
  geom_violin() +
  ylim(2.5,4) +
  theme_minimal() +
  xlab("Weeks Since Initial Play") +
  ylab("Mean Response to Survey") +
  ggtitle("Responses to S5 Survey Over Time")+
  scale_fill_viridis(option = "plasma", discrete = TRUE )
```

```{r}
week_zero <- SurveyResults %>%
  filter(weeks == 0)
week_zero_hist <- week_zero %>%
  ggplot(mapping = aes(x = S5_mean)) +
  geom_histogram() +
  xlim(0, 4) +
  annotate("text",
       	x = mean(week_zero$S5_mean) -.25,
       	y = mean(week_zero$S5_mean) * 6,
       	label = paste("Mean =", mean(week_zero$S5_mean),
       	mean(week_zero$s5_mean)),
       	col = "red",
       	size = 4)

week_three <- S5_scores_cleaned %>%
  filter(weeks == 3)
week_three_hist <- week_three %>%
  ggplot(mapping = aes(x = S5_mean)) +
  geom_histogram()

week_six <- S5_scores_cleaned %>%
  filter(weeks == 6)
week_six_hist <- week_six %>%
  ggplot(mapping = aes(x = S5_mean)) +
  geom_histogram()

week_twelve <- S5_scores_cleaned %>%
  filter(weeks == 12)
week_twelve_hist <- week_twelve %>%
  ggplot(mapping = aes(x = S5_mean)) +
  geom_histogram()

week_twenty_four <- S5_scores_cleaned %>%
  filter(weeks == 24)
week_twenty_four_hist <- week_twenty_four %>%
  ggplot(mapping = aes(x = S5_mean)) +
  geom_histogram() +
  xlim(0, 4) +
  annotate("text",
       	x = mean(week_twenty_four$S5_mean) -.25,
       	y = mean(week_twenty_four$S5_mean) * 3,
       	label = paste("Mean =", mean(week_twenty_four$S5_mean),
       	mean(week_twenty_four$s5_mean)),
       	col = "red",
       	size = 4)


grid.arrange(week_zero_hist, week_twenty_four_hist, ncol = 1)

#S5_scores_cleaned %>%
 # ggplot(mapping = aes(x = weeks, y = S5_mean)) +
  #geom_jitter()
```

```

```{r}
rm(unique_survey_scores)
```
And
```{r}
logs <- gamer
logs_short <- select(logs, -c(29:32, 42, 98:105)) # Cut out some unecessary stuff

people_sense <- subset(logs_short, event_id > 909 & event_id < 912) # Only people minigame
people_sense <- select(people_sense, c(1:3, 5, 7:8, 10:11, 15, 22, 38, 53, 56:62)) # Only people minigame part 2

player_1_sense <- subset(people_sense, player_id == 6427001 & event_id > 909 & event_id < 912) # Player 1 people sense minigame

people_sense$session <- factor(people_sense$session, levels = c("Session 1", "Session 2", "Session 3", "Session 4", "Session 5", "Session 6", "Session 7", "Session 8", "Session 9", "Session 10", "Session 11", "Session 12")) # Ordering Session numbers

ggplot(data = subset(people_sense, !is.na(session) & missed_safe_invitations > -1), mapping = aes(x = session, y = total_strikes, color = as.character(missed_safe_invitations))) + 
  geom_jitter() + 
  coord_flip() # Scatter of missed safe invitations by session

table(people_sense$total_strikes, people_sense$session) # Table of total strikes by session
table(people_sense$total_strikes, people_sense$minigame_level) # Table of total strikes by minigame level
```

```{r}
rm(logs)
rm(logs_short)
rm(player_1_sense)
rm(people_sense)
```

Alx

```